\clearpage
\newpage
\begin{thebibliography}{20} %1 should be replaced with number of citations
\singlespacing

\bibitem{bib:pauli}
W. Pauli, Phys. Today 31N9 (1978) 27

\bibitem{bib:fermi}
E. Fermi, Z. Phys. 88, 161 (1934)

\bibitem{bib:cowan}
  C. L. Cowan, Jr., F. Reines, et al., \emph{Detection of the Free Neutrino: a Confirmation}, \\
  \texttt{http://science.sciencemag.org/content/sci/124/3212/103.full.pdf}

\bibitem{bib:ray0}
Davis, Raymond, and Don S. Harmer. ``Solar Neutrinos." Solar Neutrinos. (1964): n. page. Print.

\bibitem{bib:rayreview}
Cleveland, Bruce T., et al. ``Measurement of the Solar Electron Neutrino Flux with the Homestake Chlorine Detector." ApJ. 496.505 (1998): n. page. Print.

\bibitem{bib:kam0}
Hirata, K. S., et al. ``Real-time, directional measurement of 8 solar neutrinos in the Kamiokande II detector." Phys. Rev. D. 44.2241 (1991): n. page. Print.

\bibitem{bib:sno}
McGregor, Gordon A. ``FIRST RESULTS FROM THE SUDBURY NEUTRINO OBSERVATORY." arXiv. (2002): n. page. Print.

\bibitem{bib:gal0}
Hampel, W., et al. ``GALLEX solar neutrino observations: Results for GALLEX IV." Phys. Lett. B. 447. (1999): 127-133. Print.

\bibitem{bib:gal2}
Hampel, W., et al. ``Final results of the 51Cr neutrino source experiments in GALLEX." Phys. Lett.. 420.1-2 (1998): 114-126. Print.

\bibitem{bib:sage}
Abdurashitov, J. N., et al. ``The Russian-American Gallium Experiment (SAGE) Cr Neutrino Source Measurement."  Phys. Rev. Lett. (1996): n. page. Print.

\bibitem{bib:bugey}
Declais, Y., et al. \emph{Study of reactor antineutrino interaction with proton at Bugey nuclear power plant},\\
  \texttt{ https://inspirehep.net/record/39502/}

\bibitem{bib:rovno}
Kuvshinnikov, L. A., et al. \emph{Precise measurement of the cross section for the reaction $\overline{\nu_e}$ + p $\rightarrow$ n + $e^+$ at a reactor of the Rovno nuclear power plant},\\
  \texttt{http://www.jetpletters.ac.ru/ps/1248/article\_18875.pdf}

\bibitem{bib:improvedReactor}
Mueller, Th. A., et al. \emph{Improved Predictions of Reactor Antineutrino Spectra},\\
  \texttt{https://arxiv.org/pdf/1101.2663.pdf}

\bibitem{bib:reactorGeneral}
Mention, G., et al. \emph{The Reactor Antineutrino Anomaly},\\
  \texttt{https://arxiv.org/pdf/1101.2755.pdf}

\bibitem{bib:lsnd}
Aguilar, A., et al. \emph{Evidence for Neutrino Oscillations from the Observation of Electron Anti-neutrinos in a Muon Anti-Neutrino Beam.} Phys. Rev. D. (2001): n. page. Print.

\bibitem{bib:miniboone}
MiniBooNE Collaboration. ``The Neutrino Flux prediction at MiniBooNE." Phys. Rev. D. (2008): n. page. Print.

\bibitem{bib:warwick}
Boyd, Steve. ``Neutrino Oscillations." PX435 Neutrino Physics. N.p.. Web. 19 Feb 2015. http://www2.warwick.ac.uk/fac/sci/physics/current/teach/modulei\_home/px435/lec\_oscillations.pdf.

\bibitem{bib:donut}
DONUT Collaboration, Phys. Lett. B 504 (2001) 218 [hep-ex/0012035].

\bibitem{bib:cdf}
CDF Collaboration, \emph{Observation of Top Quark Production in p $\overline{p}$ Collusions with the Collider Detector at Fermilab},\\
  \texttt{http://journals.aps.org/prl/abstract/10.1103/PhysRevLett.74.2626}


\bibitem{bib:forces}
Strassler, Matt. \emph{Of Particular Significance},\\
  \texttt{https://profmattstrassler.com/articles-and-posts/particle-physics-basics/the-known-forces-of-nature/the-strength-of-the-known-forces}

\bibitem{bib:gzeller}
J.A. Formaggio and G. P. Zeller \emph{From eV to EeV: Neutrino Cross Sections Across Energy Scales},\\
\texttt{https://arxiv.org/pdf/1305.7513.pdf}

\bibitem{bib:rein_sehgal}
D. Rein and L. M. Sehgal, \emph{Neutrino-Excitation of Baryon Resonances and Single Pion Production},\\
\texttt{Ann. Phys. (N.Y.) 133, 79 (1981).}


\bibitem{bib:genie}
  C. Andreopoulos et al., \emph{The GENIE Neutrino Monte Carlo Generator}, \\
  \texttt{http://aip.scitation.org/doi/pdf/10.1063/1.457108}


\bibitem{bib:bodek_ritchie}
A. Bodek and J.L. Ritchie, \emph{Further Studies of Fermi Motion Effects in Lepton Scattering from Nuclear Targets},\\
\texttt{https://inspirehep.net/record/164738?ln=en}


\bibitem{bib:bodek_yang0}
A. Bodek and U. K. Yang, \emph{Higher twist scaling $\xi_\omega$ and effective LO PDFs for lepton scattering},\\
\texttt{http://cds.cern.ch/record/585627/files/0210024.pdf}

\bibitem{bib:bodek_yang1}
A. Bodek and U. K. Yang, \emph{Parton Distributions, d/u, and Higher Twist Effects at High x},\\
\texttt{https://journals.aps.org/prl/abstract/10.1103/PhysRevLett.82.2467}

\bibitem{bib:llewellyn}
 C. H. Llewellyn Smith, \emph{Neutrino reactions at accelerator energies},
\texttt{https://inspirehep.net/record/67183/files/slac-pub-0958b.pdf}


\bibitem{bib:martini_mec}
 M. Martini, M. Ericson, et al., \emph{A unified approach for nucleon knock-out, coherent and incoherent pion production in neutrino interactions with nuclei},
\texttt{https://arxiv.org/pdf/0910.2622.pdf}

%\bibitem{bib:katori}
% T. Katori, \emph{Meson Exchange Current (MEC) Models in Neutrino Interaction Generators},
%\texttt{https://arxiv.org/abs/1304.6014}

\bibitem{bib:katori_martini}
 T. Katori and M. Martini, \emph{Neutrino-Nucleus Cross Sections for Oscillation Experiments},
\texttt{https://arxiv.org/pdf/1611.07770.pdf}





\bibitem{bib:weak_current}
Halzen, F., Martin, Alan D. \emph{Quarks and Leptons: An Introductory Course in Modern Particle Physics},\\
  \texttt{http://www.phy.olemiss.edu/~hamed/Quarks\_and\_Leptons.pdf}


\bibitem{bib:ANL1}
  S. B. Barish et al., Phys. Rev. D., 19, 2521 (1979).

\bibitem{bib:ANL2}
 G. M. Radecky et al., Phys. Rev. D., 25, 1161 (1982)
 
\bibitem{bib:BNL}
 T. Kitagaki et al., Phys. Rev. D., 34, 2554 (1986)
 
\bibitem{bib:HE_unknown1}
 D. Allasia et al., Nucl. Phys. B., 343, 285 (1990).

\bibitem{bib:HE_unknown2}
 H. J. Grabosch et al., Zeit. Phys. C., 41, 527 (1989).

\bibitem{bib:numucc_miniboone}
  A. A. Aguilar-Arevalo, et al., \emph{Measurement of $\nu_\mu$-induced charged-current neutral pion production cross sections on mineral oil at $E_\nu$ = 0.5-2.0 GeV},\\
  \texttt{https://arxiv.org/pdf/1010.3264v4.pdf}

\bibitem{bib:miniboone_thesis}
  Robert H. Nelson, Thesis, \emph{A Measurement of Neutrino-Induced Charged-Current Neutral Pion Production},\\
  \texttt{https://www-boone.fnal.gov/publications/Papers/rhn\_thesis.pdf}
  
\bibitem{bib:sciboone_thesis}
  Joan Catala Perez, Thesis, \emph{Measurement of neutrino induced charged current neutral pion production cross section at SciBooNE.},\\
  \texttt{http://lss.fnal.gov/archive/thesis/2000/fermilab-thesis-2014-03.pdf}  

\bibitem{bib:minerva_thesis}
  Jose Luis Palomino Gallo, Thesis, \emph{First Measurement of $\overline{\nu_\mu}$ of Induced Charged-Current $\pi^0$ Production Cross Sections on Polystyrene at $E_{\overline{\nu_\mu}}$ 2-10 GeV},\\
  \texttt{http://inspirehep.net/record/1247736/files/fermilab-thesis-2012-56.pdf}  
  
\bibitem{bib:minerva_paper}
   \emph{Single neutral pion production by charged current $\overline{\nu_\mu}$ interactions on hydrocarbon at $< E_\nu >$ =3.6 GeV},\\
  \texttt{http://www.sciencedirect.com/science/article/pii/S0370269315005493}  
  
\bibitem{bib:minerva_paper_2017}
   \emph{Measurement of charged-current single $\pi^0$ production on hydrocarbon in the few-GeV range using MINERvA },\\
  \texttt{https://arxiv.org/pdf/1708.03723.pdf}

\bibitem{bib:minerva_thesis_2017}
   \emph{Measurement of Muon Neutrino Charged Current Single $\pi^0$ Production on Hydrocarbon using MINERvA },\\
  \texttt{http://inspirehep.net/record/1592323/files/fermilab-thesis-2017-08.pdf}

  
\bibitem{bib:k2k_paper}
  C. Mariani, et al., \emph{Measurement of inclusive $\pi^0$ production in the Charged-Current Interactions of Neutrinos in a 1.3-GeV wide band beam},\\
  \texttt{arXiv:1012.1794}


\bibitem{bib:anderson}
Anderson, Colin. ``Measurement of Muon Neutrino and AntiNeutrino Induced Single Neutral Pion Production Cross Section." Thesis. (2011): n. page. Print.

\bibitem{bib:uboone_proposal}
  The MicroBooNE Collaboration, \emph{A Proposal for a New Experiment Using the Booster and NuMI Neutrino Beamlines: MicroBooNE},\\
  \texttt{http://www-microboone.fnal.gov/public/MicroBooNE\_10152007.pdf}

\bibitem{bib:uboone_JINST}
  The MicroBooNE Collaboration, \emph{Design and Construction of the MicroBooNE Detector},\\
  \texttt{https://arxiv.org/pdf/1612.05824v2.pdf}

\bibitem{bib:surge}
  J. Asaadi, et al., \emph{Testing of High Voltage Surge Protection Devices for Use in Liquid Argon TPC Detectors}, \\
  \texttt{https://arxiv.org/pdf/1406.5216v2.pdf}

\bibitem{bib:tdr}
  The MicroBooNE Collaboration, \emph{The MicroBooNE Technical Design Report}, \\
  \texttt{http://www-microboone.fnal.gov/publications/TDRCD3.pdf}


\bibitem{bib:first_nus}
  The MicroBooNE Collaboration, \emph{First Neutrino Interactions Observed with the MicroBooNE Liquid-Argon TPC Detector},\\
  \texttt{http://www-microboone.fnal.gov/publications/publicnotes/MICROBOONE-NOTE-1002-PUB.pdf}

\bibitem{bib:ben_jones}
  Benjamin J.P. Jones, Thesis, \emph{Steril Neutrinos in Cold Climates},\\
  \texttt{https://inspirehep.net/record/1389805/files/fermilab-thesis-2015-17.pdf}

\bibitem{bib:sorel}
  M. Sorel, \emph{Expected performance of an ideal liquid argon neutrino detector with enhanced sensitivity to scintillation light}, \\
  \texttt{https://arxiv.org/pdf/1405.0848.pdf}

\bibitem{bib:lumin}
  M. Sorel, \emph{Argon, kryton, and xenon excimer luminescence: From the dilute gas to the condensed phase}, \\
  \texttt{http://aip.scitation.org/doi/pdf/10.1063/1.457108}
  
  \bibitem{bib:purity}
  The MicroBooNE Collaboration, \emph{Measurement of the Electronegative Contaminants and Drift Electron Lifetime in the MicroBooNE Experiment},\\
  \texttt{http://www-microboone.fnal.gov/publications/publicnotes/MICROBOONE-NOTE-1003-PUB.pdf}

\bibitem{bib:purity2}
  R. Acciarri, et al., \emph{Liquid Argon Dielectric Breakdown Studies with the MicroBooNE Purification System}, \\
  \texttt{https://arxiv.org/pdf/1408.0264v1.pdf}
  
\bibitem{bib:root}
  Rene Brun, Fons Rademakers., \emph{ROOT Documentation}, \\
  \texttt{https://root.cern/documentation}
  
\bibitem{bib:geant4}
  S. Agostinelli et al., \emph{Geant4--a simulation toolkit},\\
  \texttt{http://www.sciencedirect.com/science/article/pii/S0168900203013688}
  
\bibitem{bib:corsika}
  D. Heck and T. Pierog, \emph{Extensive Air Shower Simulation with CORSIKA: A User's Guide},\\
  \texttt{https://web.ikp.kit.edu/corsika/usersguide/usersguide.pdf}
  

\bibitem{bib:pubnote_cosmic}
  The MicroBooNE Collaboration, \emph{Cosmic Shielding Studies},\\
  \texttt{http://microboone.fnal.gov/wp-content/uploads/MICROBOONE-NOTE-1005-PUB.pdf}
  
  
\bibitem{bib:gdml}
  R. Chytracek, J. McCormick, W. Pokorski, and G. Santin, \emph{Geometry Description Markup Language for Physics Simulation and Analysis Applications}, \\
  \texttt{http://ieeexplore.ieee.org/document/1710291}

\bibitem{bib:noise}
  The MicroBooNE Collaboration, \emph{Noise Characterization and Filtering in the MicroBooNE TPC},\\
  \texttt{http://www-microboone.fnal.gov/publications/publicnotes/MICROBOONE-NOTE-1016-PUB.pdf}

\bibitem{bib:pandora}
  The MicroBooNE Collaboration, \emph{The Pandora multi-algorithm approach to automated pattern recognition in LArTPC detectors},\\
  \texttt{http://www-microboone.fnal.gov/publications/publicnotes/MICROBOONE-NOTE-1015-PUB.pdf}


% Analysis References
%\bibitem{bib:normdatamc}
% Anne Schukraft, \emph{How to normalize data and MC},\\
% \texttt{http://microboone-docdb.fnal.gov:8080/cgi-bin/ShowDocument?docid=5640}
% 
%\bibitem{bib:davidcpot}
%  David Caratelli, \emph{POT Normalized BNB Beam Flash Time Distribution
%2 DATA/MC Comparison},\\
%  \texttt{https://microboone-docdb.fnal.gov/cgi-bin/private/ShowDocument?docid=9614}
%
%\bibitem{bib:jaz_datamc_agreement}
%  Joseph Zennamo, \emph{Investigating Selection2
%Data-to-Simulation Agreement},\\
%  \texttt{https://microboone-docdb.fnal.gov/cgi-bin/private/ShowDocument?docid=11963}
%
%\bibitem{bib:zarkopot}
%  Zarko Pavlovic, \emph{Trigger Counts and Protons On Target},\\
%  \texttt{https://microboone-docdb.fnal.gov/cgi-bin/private/RetrieveFile?docid=11507\&filename=uboonePOT.pdf\&version=1}
%
%\bibitem{bib:numucc}
%  Rui An, et al., \emph{numu CC inclusive - internal note - MICROBOONE-NOTE-1010-INT}, DocDB 5851,\\
%  \texttt{http://microboone-docdb.fnal.gov:8080/cgi-bin/ShowDocument?docid=5851}
% 
%\bibitem{bib:6172}
%  Tngjun Yang, \emph{Numu CC Inclusive Analysis Highlights and Plans}, DocDB 6172,\\
%  \texttt{http://microboone-docdb.fnal.gov:8080/cgi-bin/ShowDocument?docid=6172}
%
%\bibitem{bib:mcc8_val}
% MicroBooNE Collaboration, \emph{MCC8 Validations},\\
% \texttt{http://microboone-docdb.fnal.gov:8080/cgi-bin/ShowDocument?docid=7066}
%
%\bibitem{bib:kazu_optical_bug}
% Kazu Terao, \emph{Debugging Larsoft Optical Simulation},\\
%
%\bibitem{bib:marco_selection}
% Marco Del Tutto, \emph{Status of the $\nu_\mu$ CC
%Inclusive Event Selection},\\
% \texttt{https://microboone-docdb.fnal.gov/cgi-bin/private/ShowDocument?docid=11159}

\bibitem{bib:jz_unblinding_note}
 Ariana Hackenburg and Joseph Zennamo, \emph{Request to Open Run 1 Data with Modified Selection II},\\
 \texttt{https://microboone-docdb.fnal.gov/cgi-bin/private/ShowDocument?docid=11645}
 
% \bibitem{bib:jarrett_opticalprecut}
%  Jarrett Moon, \emph{Optical Precuts for
%Low PE Noise Removal}, DocDB 7779,\\
%\texttt{https://microboone-docdb.fnal.gov/cgi-bin/private/RetrieveFile?docid=7779\&filename=2-30-17DLReview\_PreCuts.pdf\&version=3}

\bibitem{bib:davidc_hitremoval}
  David Caratelli, \emph{Shower Reconstruction : Hit Removal in $\nu_{\mu}$ CC interactions},\\
  \texttt{https://microboone-docdb.fnal.gov/cgi-bin/private/RetrieveFile?docid=9020\&filename=HitRemoval\_TN.pdf\&version=8}

%\bibitem{bib:mcc83_validation_plots}
%  Adam Lister and Daniel Devitt, \emph{MCC8.3 Data/MC Comparisons},\\
%  \texttt{https://microboone-docdb.fnal.gov/cgi-bin/private/RetrieveFile?docid=11852\&filename=testScript.pdf\&version=4} 
  
\bibitem{bib:opencv}
  \emph{OpenCV Documentation},\\
  \texttt{http://opencv.org/documentation.html}

%\bibitem{bib:5864}
%  Rui An, et al., \emph{Reconstruction of $\pi^0 \rightarrow \gamma\gamma$ decays from $\nu_\mu$ charged current interactions in data }, DocDB 5864,\\
%   \texttt{http://microboone-docdb.fnal.gov:8080/cgi-bin/ShowDocument?docid=5864}
%
%\bibitem{bib:5856}
%   Vic Genty, et al., \emph{Golden $\pi^0$ Clustering }, DocDB 5856,\\
%   \texttt{http://microboone-docdb.fnal.gov:8080/cgi-bin/ShowDocument?docid=5856}

\bibitem{bib:linearPolar}
  OpenCV linearPolar Algorithm Documentation, \\
  \texttt{http://docs.opencv.org/2.4/modules/imgproc/doc/geometric\_transformations.html\#linearpolar}

\bibitem{bib:structuringElement}
  OpenCV Structuring Element Algorithm Documentation, \\
  \texttt{http://docs.opencv.org/2.4/modules/imgproc/doc/filtering.html\#getstructuringelement}

\bibitem{bib:dilate}
  OpenCV Dilation Algorithm Documentation, \\
  \texttt{http://docs.opencv.org/2.4/modules/imgproc/doc/filtering.html\#dilate}

\bibitem{bib:blur}
  OpenCV Blur Algorithm Documentation, \\
  \texttt{http://docs.opencv.org/2.4/modules/imgproc/doc/filtering.html\#dilate}
  
\bibitem{bib:thresholding}
  OpenCV Thresholding Algorithm Documentation, \\
  \texttt{http://docs.opencv.org/2.4/modules/imgproc/doc/miscellaneous\_transformations.html?highlight=threshold\#threshold}
  
\bibitem{bib:contourFinding}
  OpenCV Contour Finding Algorithm Documentation, \\
  \texttt{http://docs.opencv.org/2.4/modules/imgproc/doc/structural\_analysis\_and\_shape\_descriptors.html?highlight=findcontours\#findcontours}

%\bibitem{bib:calibration_ref}
%  Dead channel information, dat file, \\
%  \texttt{https://cdcvs.fnal.gov/redmine/projects/uboonecode/repository/changes/uboone/Calibrations/calibrationList\_channelStatus\_mcc8\_v1r4\_1457127268.dat?rev=v06\_26\_01\_10}

\bibitem{bib:pdg_radiationlength}
  Atomic Nuclear Properties of Liquid Argon, \\
  \texttt{http://pdg.lbl.gov/2017/AtomicNuclearProperties/HTML/liquid\_argon.html}

\bibitem{bib:minAreaRect}
  OpenCV Min Area Rectangle, \\
  \texttt{http://docs.opencv.org/2.4/modules/imgproc/doc/structural\_analysis\_and\_shape\_descriptors.html?highlight=minarearect\#minarearect}

\bibitem{bib:convexHull}
  OpenCV Convex Hull, \\
  \texttt{http://docs.opencv.org/2.4/modules/imgproc/doc/structural\_analysis\_and\_shape\_descriptors.html?highlight=convexhull\#convexhull}

\bibitem{bib:larliteGeoHelper}
  LArLite Repository, \\
\texttt{https://github.com/larlight/larlite/blob/trunk/core/LArUtil/GeometryHelper.cxx}


\bibitem{bib:davidc_energycalibration}
  David Caratelli, \emph{Shower and $\pi^0$ Reconstruction in $\nu_{\mu}$ CC Interactions},\\
  \texttt{https://microboone-docdb.fnal.gov/cgi-bin/private/RetrieveFile?docid=9020\&filename=main.pdf\&version=8}

\bibitem{bib:ionization_per_electron}
 M.E. Shibamura et al., \emph{Drift velocities of electrons, saturation characteristics of ionization
and W-values for conversion electrons in liquid argon, liquid argon-gas mixtures and liquid
xenon, Nucl. Instrumentation Meth., 131, (1975) p249}

%\bibitem{bib:davidc_energycalibration_gain}
%  David Caratelli, \emph{Calibration of the MicroBooNE TPC’s Energy Response with Stopping Muons},\\
%  \texttt{https://microboone-docdb.fnal.gov/cgi-bin/private/RetrieveFile?docid=9149\&filename=calibration-microboone-tpcs.pdf\&version=1}


 \bibitem{bib:davidc_recomb}
  David Caratelli, et al., \emph{Demonstration of Electro-Magnetic Shower Reconstruction with the MicroBooNE LArTPC from Neutrino-induced $\pi^0$ Decay},\\
\texttt{https://microboone-docdb.fnal.gov/cgi-bin/private/RetrieveFile?docid=6866\&filename=v1\_2.pdf\&version=11}
  
 \bibitem{bib:argoneut_recomb}
  ArgoNeuT Collaboration, \emph{A study of electron recombination using highly ionizing particles in the ArgoNeuT Liquid Argon TPC},\\
  Journal of Instrumentation (JINST), Vol 8, P08005, \texttt{http://arxiv.org/abs/1306.1712}
  
\bibitem{bib:davidc_hitthresholding}
  David Caratelli, \emph{Hit Thresholding Impact on EM Shower Energy Reconstruction},\\
  \texttt{https://microboone-docdb.fnal.gov/cgi-bin/private/RetrieveFile?docid=9020\&filename=HitThresholding\_TN.pdf\&version=8}

\bibitem{bib:davidc_missingE}
  David Caratelli, et al., \emph{Demonstration of Electro-Magnetic Shower Reconstruction with
the MicroBooNE LArTPC from Neutrino-induced $\pi^0$ Decays},\\
  \texttt{https://microboone-docdb.fnal.gov/cgi-bin/private/RetrieveFile?docid=6866\&filename=v1\_2.pdf\&version=11}
  
\bibitem{bib:jz_catch_subleading}
  Joseph Zennamo, \emph{$\pi^0$ Sub-leading Photon Finder: Outlook},\\
  \texttt{https://microboone-docdb.fnal.gov/cgi-bin/private/ShowDocument?docid=10907}
 
  
\bibitem{bib:timb_singleshower}
  Varun Mathur and Tim Bolton, \emph{Particle Discrimination vs. Particle Identification in MicroBooNE},\\
  \texttt{https://microboone-docdb.fnal.gov/cgi-bin/private/RetrieveFile?docid=9311\&filename=particlediscriminationvsparticleid.pdf\&version=2}

\bibitem{bib:nist}
 NIST Database, \emph{Thermophysical Properties of Fluid Systems},\\
  \texttt{http://webbook.nist.gov/chemistry/fluid/}

\bibitem{bib:flux}
  Beam Working Group, \emph{Flux Files}\\
  \texttt{https://cdcvs.fnal.gov/redmine/projects/ubooneoffline/wiki/Flux\_Histograms}

\bibitem{bib:genie}
  Costas Andreopoulos, et al., \emph{The GENIE Neutrino Monte Carlo Generator PHYSICS \& USER MANUAL},\\
  \texttt{https://arxiv.org/pdf/1510.05494.pdf}

%\bibitem{bib:larlite}
%  Kazu Terao, \emph{LArLite User Manual},\\
%  \texttt{https://microboone-docdb.fnal.gov/cgi-bin/private/RetrieveFile?docid=3183}

\bibitem{bib:flux_uncertainty_tn}
  Zarko Pavlovich and Joseph Zennamo, \emph{MicroBooNE Flux Uncertainty Implementation},\\
  \texttt{https://microboone-docdb.fnal.gov/cgi-bin/private/ShowDocument?docid=8622}

\bibitem{datacosflux} 
Leonidas Kalousis, \emph{Cosmic muon flux measurements at the Liquid Argon Test Facility}, \\DocDB 3130, Jan. 2014. 

\bibitem{mccosflux} 
MicroBooNE Collaboration, \emph{Cosmic Shielding Studies at MicroBooNE}, \\ MicroBooNE Public Note 1005, May 2016.


\end{thebibliography}
